TBD

### 2021-02-21 outputs/paper/paper.Rmd
Edit text

Pearson’s Chi-squared (*X*^2^) test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is close to 0 (*p* < 2.2e-16), meaning that there is a high correlation between those two variables. Consequently, it is expected that restaurants will adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.

>>>>

Pearson’s Chi-squared (*X*^2^) test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is close to 0, meaning that there is a high correlation between those variables. Consequently, it is expected that restaurants will most likely adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.
